Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2018-12-17 SI.tex
More minor changes to SI and manu

We calculate the frequency-dependent dielectric properties of hBN with
varying supperlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$
with electron-hole interaction (G$_{0}$W$_{0}$+BSE). As shown in
Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out}, the
intensities of $\varepsilon_{\mathrm{SL}}^{\parallel}(\omega)$ and
$\varepsilon_{\mathrm{SL}}^{\perp}(\omega)$ reduce with increasing $L$
throughout the whole frequency range. The $L$-dependency can also be
removed using Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def}, yielding lattice-independent
polarizabilities throughout the frequency domain.

\begin{figure}[H]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-in_plane.pdf}
 \caption{Dependence of in-plane dielectric properties on $L$ for
   monolayer BN calculated using PBE method: \textbf{a} Real part of
   $\varepsilon_{\mathrm{SL}}^{\parallel}$, \textbf{b} Real part of
   $\alpha_{\mathrm{2D}}^{\parallel}$, \textbf{c} Imaginary part of
   $\varepsilon_{\mathrm{SL}}^{\parallel}$, \textbf{d} Imaginary part
   of $\alpha_{\mathrm{2D}}^{\parallel}$.  The same {\bf k}-sampling
   is used in all simulations with the only variable quantity being
   $L$. Clearly, the $L$-dependency of the superlattice dielectric
   function is removed using 2D polarizabilities.}
  \label{fig:PBE-omega-in}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-out_of_plane.pdf}
  \caption{Dependence of out-of-plane dielectric properties on $L$ for
    monolayer BN calculated using PBE method: \textbf{a} Real part of
    $\varepsilon_{\mathrm{SL}}^{\perp}$, \textbf{b} Real part of
    $\alpha_{\mathrm{2D}}^{\perp}$, \textbf{c} Imaginary part of
    $\varepsilon_{\mathrm{SL}}^{\perp}$, \textbf{d} Imaginary part of
    $\alpha_{\mathrm{2D}}^{\perp}$.  The same {\bf k}-sampling is used
    in all simulations with the only variable quantity being
    $L$. Clearly, the $L$-dependency of the superlattice dielectric
    function is removed using 2D polarizabilities.}
  \label{fig:PBE-omega-out}
\end{figure}

We note that the result may change slightly when G$_{0}$W$_{0}$ method
is used. As shown in Figures \ref{fig:GW-omega-in} and
\ref{fig:GW-omega-out}, not only do the intensity of the dielectric
functions change with $L$, but also the peak positions. As a result
the obtained polarizabilities also show $L$-dependent peak shift. This
can be explained by the long-range nature of Coulomb interactions. In
fact the self-energy of the G$_{0}$W$_{0}$ system $\Sigma$, is determined by:
\begin{equation}
  \label{eq:GW-formula}
  \Sigma = i G_{0} W_{0} = i G_{0} \varepsilon^{-1} \nu
\end{equation}
where $G$ is the non-interacting Green function, and $\nu$ is the
Coulomb interaction. Since the dielectric constant $\varepsilon$
changes with $L$, the self energy as well quasi-particle energies of
the G$_{0}$W$_{0}$ method also varies with $L$. As a result we get
higher peak energy of the dielectric spectrum when $L$ increases. Such
peculiar $L$-dependency can be minimized when adding electron-hole
interaction through the Bethe-Salpethe equation (BSE), as shown in
Figures \ref{fig:BSE-omega-in} and \ref{fig:BSE-omega-out}. The
polarizabilities again becomes lattice-independent due to the
localization of excitons within the 2D material layer, which corrects the energy shift of G$_{0}$W$_{0}$ method.

@@

\begin{figure}[H]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-in_plane.pdf}
 \caption{Similar to Figure \ref{fig:PBE-omega-in} but calculated
   using G$_{0}$W$_{0}$ method. A shift of peak position (frequency)
   in the dielectric function spectra is observed, resulted from the
   change of quasi-particle energy in G$_{0}$W$_{0}$ calculations
   invloving the 2D slab.}
  \label{fig:GW-omega-in}
\end{figure}

\begin{figure}[H]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-out_of_plane.pdf}
 \caption{Similar to Figure \ref{fig:PBE-omega-out} but calculated
   using G$_{0}$W$_{0}$ method.  A shift of peak position (frequency)
   in the dielectric function spectra is observed, resulted from the
   change of quasi-particle energy in G$_{0}$W$_{0}$ calculations
   invloving the 2D slab.}
  \label{fig:GW-omega-out}
\end{figure}

\begin{figure}[H]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-BSE-in_plane.pdf}
 \caption{Similar as in Fig. \ref{fig:GW-omega-in} but taking into
   account electron-hole interactions at the level of the
   Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE).  The peak shift
   in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$. As a
   result the polarizabilities becomes almost independent of $L$,
   consistent to results obtained by the PBE method.}
  \label{fig:BSE-omega-in}
\end{figure}

\begin{figure}[H]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-BSE-out_of_plane.pdf}
 \caption{Similar as in Fig. \ref{fig:GW-omega-out} but taking into
   account electron-hole interactions at the level of the
   Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE).  As a result
   the polarizabilities becomes almost independent of $L$, consistent
   to results obtained by the PBE method.  }
  \label{fig:BSE-omega-out}
\end{figure}

@@

separation between the 2D and 3D regimes in the Figure

@@

\section{Raw data from first principles calculations}
\subsection{Quantities from first principles calculation}
\label{sec:raw}
\todo[inline]{I think showing the $\alpha$ values is enough since
  whoever interested in calculating the $r_{0}$ values can simply
  multiply them by $2 \pi$. }
\input{raw_data}

>>>>

We calculate the frequency-dependent dielectric properties of hBN with
varying supperlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$
with electron-hole interaction (G$_{0}$W$_{0}$+BSE). As shown in
Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out}, the
intensities of $\varepsilon_{\mathrm{SL}}^{\parallel}(\omega)$ and
$\varepsilon_{\mathrm{SL}}^{\perp}(\omega)$ reduce with increasing $L$
throughout the whole frequency range. The $L$-dependency can also be
removed using Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def}, yielding lattice-independent
polarizabilities throughout the frequency domain. Note when extracting
the frequency-dependent 2D polarizabilities from
Eqs. \ref{main-eq:alpha-para-def} and \ref{main-eq:alpha-perp-def},
the peak position from $\varepsilon_{\mathrm{SL}}$ is preserved. This
is explained by the fact that the local extrema from spectra of
$\varepsilon_{\mathrm{SL}}$ is also the local extrema in corresponding
$\alpha_{\mathrm{2D}}$, since when
$\partial \varepsilon_{\mathrm{SL}}(\omega) / \partial \omega = 0 $,
we have
\begin{subequations}
\begin{eqnarray}
  \label{eq:extrema-para}
  \frac{\partial \alpha_{\mathrm{2D}}^{\parallel}(\omega)}{\partial \omega}
  &= \varepsilon_{0}L {\displaystyle \frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0   \\
  \label{eq:extrema-perp}
  \frac{\partial \alpha_{\mathrm{2D}}^{\perp}(\omega)}{\partial \omega}
  &= \varepsilon_{0}L {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{2}}\frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0
\end{eqnarray}
\end{subequations}
which indicates that the peak position is perserved when transforming
$\varepsilon_{\mathrm{SL}}(\omega)$ to $\alpha_{\mathrm{2D}}(\omega)$.

We note that the result change slightly when G$_{0}$W$_{0}$ method
is used. As shown in Figures \ref{fig:GW-omega-in} and
\ref{fig:GW-omega-out}, not only do the intensity of the dielectric
functions change with $L$, but also the peak positions. As a result
the obtained polarizabilities also show $L$-dependent peak shift. This
can be explained by the long-range nature of Coulomb interactions. In
fact the self-energy of the G$_{0}$W$_{0}$ system $\Sigma$, is determined by:
\begin{equation}
  \label{eq:GW-formula}
  \Sigma = i G_{0} W_{0} = i G_{0} \varepsilon^{-1} \nu
\end{equation}
where $G$ is the non-interacting Green function, and $\nu$ is the
Coulomb interaction. Since the dielectric constant $\varepsilon$
changes with $L$, the self energy as well quasi-particle energies of
the G$_{0}$W$_{0}$ method also varies with $L$. As a result we get
higher peak energy of the dielectric spectrum when $L$ increases. Such
peculiar $L$-dependency can be minimized when adding electron-hole
interaction through the Bethe-Salpethe equation (BSE), as shown in
Figures \ref{fig:BSE-omega-in} and \ref{fig:BSE-omega-out}. The
polarizabilities again becomes lattice-independent due to the
localization of excitons within the 2D material layer, which corrects the energy shift of G$_{0}$W$_{0}$ method.

@@

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-in_plane.pdf}
 \caption{Dependence of in-plane dielectric properties on $L$ for
   monolayer BN calculated using PBE method: \textbf{a} Real part of
   $\varepsilon_{\mathrm{SL}}^{\parallel}$, \textbf{b} Real part of
   $\alpha_{\mathrm{2D}}^{\parallel}$, \textbf{c} Imaginary part of
   $\varepsilon_{\mathrm{SL}}^{\parallel}$, \textbf{d} Imaginary part
   of $\alpha_{\mathrm{2D}}^{\parallel}$.  The same {\bf k}-sampling
   is used in all simulations with the only variable quantity being
   $L$. Clearly, the $L$-dependency of the superlattice dielectric
   function is removed using 2D polarizabilities.}
  \label{fig:PBE-omega-in}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.9\linewidth]{img/SI-PBE-omega-out_of_plane.pdf}
  \caption{Dependence of out-of-plane dielectric properties on $L$ for
    monolayer BN calculated using PBE method: \textbf{a} Real part of
    $\varepsilon_{\mathrm{SL}}^{\perp}$, \textbf{b} Real part of
    $\alpha_{\mathrm{2D}}^{\perp}$, \textbf{c} Imaginary part of
    $\varepsilon_{\mathrm{SL}}^{\perp}$, \textbf{d} Imaginary part of
    $\alpha_{\mathrm{2D}}^{\perp}$.  The same {\bf k}-sampling is used
    in all simulations with the only variable quantity being
    $L$. Clearly, the $L$-dependency of the superlattice dielectric
    function is removed using 2D polarizabilities.}
  \label{fig:PBE-omega-out}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-in_plane.pdf}
 \caption{Similar to Figure \ref{fig:PBE-omega-in} but calculated
   using G$_{0}$W$_{0}$ method. A shift of peak position (frequency)
   in the dielectric function spectra is observed, resulted from the
   change of quasi-particle energy in G$_{0}$W$_{0}$ calculations
   invloving the 2D slab.}
  \label{fig:GW-omega-in}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-omega-out_of_plane.pdf}
 \caption{Similar to Figure \ref{fig:PBE-omega-out} but calculated
   using G$_{0}$W$_{0}$ method.  A shift of peak position (frequency)
   in the dielectric function spectra is observed, resulted from the
   change of quasi-particle energy in G$_{0}$W$_{0}$ calculations
   invloving the 2D slab.}
  \label{fig:GW-omega-out}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-BSE-in_plane.pdf}
 \caption{Similar as in Fig. \ref{fig:GW-omega-in} but taking into
   account electron-hole interactions at the level of the
   Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE).  The peak shift
   in energies are reduced in comparison with G$_{\rm 0}$W$_{0}$. As a
   result the polarizabilities becomes almost independent of $L$,
   consistent to results obtained by the PBE method.}
  \label{fig:BSE-omega-in}
\end{figure}

\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-BSE-out_of_plane.pdf}
 \caption{Similar as in Fig. \ref{fig:GW-omega-out} but taking into
   account electron-hole interactions at the level of the
   Bethe-Salpeter equation (G$_{\rm 0}$W$_{0}$ - BSE).  As a result
   the polarizabilities becomes almost independent of $L$, consistent
   to results obtained by the PBE method.  }
  \label{fig:BSE-omega-out}
\end{figure}

@@

separation between the 2D and 3D regimes in  main text Figure

@@

\section{Raw data from first principles calculations}
\subsection{Quantities from first principles calculation}
\label{sec:raw}
Table S2 shows the parameters and results from the
first principles calculations for the 2D materials studied. The 2D
screening lengthes $r_{0}^{\parallel}$ and $r_{0}^{\perp}$ can be
obtained by multiplying $2 \pi$ to the columns
$\alpha_{\mathrm{2D}}^{\parallel}/(4\pi \varepsilon_{0})$ and
$\alpha_{\mathrm{2D}}^{\perp}/(4\pi \varepsilon_{0})$, respectively.

\input{raw_data}

### 2018-12-17 paper.tex
More minor changes to SI and manu

\begin{figure}[H]
\centering
\includegraphics[width=0.70\linewidth]{img/fig2.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D
    materials}. \textbf{a}. The structures of the 2D materials investigated in this study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$, $\alpha_{\mathrm{2D}}^{\perp}$
  (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
  materials studied.  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{c}. $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$
  (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the
  background. \textbf{d}. $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in
  \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
  schematically shown in the inset), showing a perfect linear relation
  with slope very close to $1/4\pi$. The universal scaling relation is
  also revealed using the C2DB database (squares), as superimposed on \textbf{c}
  and \textbf{d}.}
\end{figure}

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=0.70\linewidth]{img/fig2.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D materials}. \textbf{a}. The structures of
  the 2D materials investigated in this
  study. \textbf{b}. $\alpha_{\mathrm{2D}}^{\parallel}$,
  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
  (blue dots) for all the 2D materials studied.
  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{c}.
  $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the background. \textbf{d}.
  $\alpha_{\mathrm{2D}}^{\perp}/(4\pi\varepsilon_{0})$ (in \AA{}) as a
  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
  in the inset), showing a perfect linear relation with slope very
  close to $1/4\pi$ (i.e.
  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
  revealed using the data from Ref. \citenum{Haastrup_2018} (squares),
  as superimposed on \textbf{c} and \textbf{d}.}
\end{figure}
